\documentclass[../professional-cv.tex]{subfiles}
\begin{document}
	\begin{rSection}{Work Experience}
		%----------------------------------------------------------------------------------------
		%	WORK EXPERIENCE SECTION
		%----------------------------------------------------------------------------------------
		
		\begin{rWorkSection}
			{\href{https://aimedic.co/}{AIMedic}}
			{Tehran, Iran}
			
			\vspace{-1em}
			{\em MLOps and Infrastructure Engineer} \hfill {\em Mar. 2022 - Present} \hspace{10pt}
			\normalfont
			\begin{list}{$\cdot$}{\leftmargin=10pt\normalfont \rightmargin=20pt}
				\itemsep -0.5em
				\item Led the process of developing internal tools and plugins for ML pipelines, e.g. data registry, model registry and feature store solutions. Stack: Minio, Python, FastAPI, Docker, DVC, Metaflow, MLflow, Postgres.
				\item Defined and standardized development process and led the team to implement CI pipelines for all services using Gitlab CI and Harbor.
				% \item Had full ownership of changing service architectures from monolith to service based and micro services, which boosted the successful deployments rate by 200\% in the following quarter.
				\item Led the team to change the service architectures from monolith to service based, which increased successful deployment rates by 50\% in the next quarter.
				\item Designed and led the team to implement an AI as a service platform in order to integrate all provided services together, which boosted the deployment frequency by 30\% in the following quarter.
				\item Designed and led the team to implement a training as a service platform for internal ML training pipelines, which boosted our training time fficiency by 30\% compared to the simple queued submissions.
				\item Deployed containerized services using Docker, Kubernetes and Anisble.
				\item Maintained, and monitored deployed services using Grafana, Prometheus and Loki.
				\item Administrated bare-metal infrastructure in the inter-company private cloud solution using ProxMox.
						
			\end{list}
			{\em ML Team Lead} \hfill {\em Aug. 2021 - Mar. 2022}
			\normalfont
			\begin{list}{$\cdot$}{\leftmargin=10pt\normalfont \rightmargin=20pt}
				\itemsep -0.5em
				\item Led the team to develop ML solutions for arrhythmic ECG and epileptic EEG classification tasks. Stack: PyTorch, MNE, Pandas, HDF5.
				\item Led the team to develop and deploy webservices for signal classification AI solutions. Stack: PyTorch, FastAPI and Docker.
				\item Implemented a hyperparameter optimization pipeline for model optimization, which resulted in a 3\% F1-score boost in the ECG classificaiton task.
			\end{list}
		\end{rWorkSection}
		
		\begin{rSubsection}
			{\href{https://hamsaa.ir}{Hamsaa}}
			{ \fmtdate{01}{2019} - \fmtdate{11}{2019} }
			{Software Engineer}
			{Tehran, Iran}
			\item Worked as a SWE on an inter-company social media solution. Stack: Java, Kotlin, Android, Git.
			\item Developed important features such as in-app video player, in-app file downloader and guided tour for on-boarding new users.
			
		\end{rSubsection}

		
	
		%----------------------------------------------------------------------------------------
	\end{rSection}
\end{document}